The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-09-08 paper/ms.tex
new appendix figures

We adopt the geometry shown in Fig~\ref{fig:scheme} to derive an analytic expression of this emerging spectrum,
Note that this geometry differs from the scheme shown in Fig~1 in the main body of
the paper. 
%
\begin{figure*}[h]
\centerline{\includegraphics[width=85mm]{fig11a.pdf}
\includegraphics[width=85mm]{fig11b.pdf}}
\caption[]{Adopted geometry for evaluating the analytic spectrum.}
\label{fig:scheme}
\end{figure*} 
%
The sightline to the observer \& rotation axis define the $x-z$ plane. 
The {\it left panel} in Fig~\ref{fig:scheme} shows the view from the $y$-axis. 
The observer sits along the $x$ axis. 
The rotation axis makes an angle $i$ with respect to the $z$-axis. 
We sum up spectra from individual patches by integrating over the
impact parameter $b$, and angle $\phi$. 
Each $(b,\phi)$ corresponds to a point on the sphere. 
This point has a velocity vector ${\bf v}(b,\phi,i)$, which we denote
with ${\bf v}$ for brevity. The magnitude of ${\bf v}$ is $|{\bf v}|=V_{\rm max}R'/R$. Here $R'=\sqrt{R^2 -s^2}$, in which $s$ denotes the distance of the point $(b,\phi)$ to the plane perpendicular to the rotation axis and through the origin (see the {\it left panel} of Fig~\ref{fig:scheme}). This distance $s$ is given by $s=|-\sin i\sqrt{R^2-b^2}+ b \cos \phi \cos i|$.\\

@@

>>>>

We adopt the geometry shown in Fig~\ref{fig:scheme} to derive an analytic expression of this emerging spectrum,
Note that this geometry differs from the scheme shown in Fig~1 in the main body of
the paper. 
%
\begin{figure*}[h]
\centerline{\includegraphics[width=80mm]{fig11a.pdf}
\includegraphics[width=80mm]{fig11b.pdf}}
\caption[]{Adopted geometry for evaluating the analytic spectrum.}
\label{fig:scheme}
\end{figure*} 
%
The sightline to the observer \& rotation axis define the $x-z$ plane. 
The {\it left panel} in Fig~\ref{fig:scheme} shows the view from the $y$-axis. 
The observer sits along the $x$ axis. 
The rotation axis makes an angle $i$ with respect to the $z$-axis. 
We sum up spectra from individual patches by integrating over the
impact parameter $b$, and angle $\phi$. 
Each $(b,\phi)$ corresponds to a point on the sphere. 
This point has a velocity vector ${\bf v}(b,\phi,i)$, which we denote
with ${\bf v}$ for brevity. The magnitude of ${\bf v}$ is $|{\bf v}|=V_{\rm max}R'/R$. Here $R'=\sqrt{R^2 -s^2}$, in which $s$ denotes the distance of the point $(b,\phi)$ to the plane perpendicular to the rotation axis and through the origin (see the {\it left panel} of Fig~\ref{fig:scheme}). This distance $s$ is given by $s=|-\sin i\sqrt{R^2-b^2}+ b \cos \phi \cos i|$.\\

@@

To further test the assumption of scattering in a rotating medium proceeding
as in a static medium we compute the distribution of the outgoing
angles $\mu$. The results are shown in Figure \ref{fig:surface}; it
shows that the distribution for $\mu$ is independent of the rotational
velocity and the location over the sphere. The only dependence comes
with $\tau_{H}$. For higher values of the optical depth the
distribution gets closer to $I(\mu)\propto \mu$ as expected for a
static medium \citep{Ahn01}.

%
\begin{figure*}[h]
\centerline{
\includegraphics[width=0.30\textwidth]{fig12a.pdf}
\includegraphics[width=0.30\textwidth]{fig12b.pdf}
\includegraphics[width=0.30\textwidth]{fig12c.pdf}}
\caption[]{Distribution of the cosine of the angle between the
  propagation direction and the sphere's surface. The distributions
  have been normalized to unity. Left panel: different rotational
  velocities; middle panel: different viewing angles; right panel:
  different optical depths. Only the optical depth has an effect on
  the outogoing directions. This is consistent with the assumption
  that \lya scattering in a medium with solid body rotation proceeds as in
  a static medium.}
\label{fig:surface}
\end{figure*} 
%
